---
title: "Playing Alone, Feeling Connected: Do Single-Player Video Games with Social Surrogates Replenish Belonging After Social Rejection?"
author: "Naoyuki Sunami"
abstract: "People have a fundamental need to belong—to be accepted, loved, and cared for. The COVID-19 pandemic has threatened people’s sense of belonging; people had to isolate themselves from others due to the stay-at-home orders. At the same time in early 2020, people started to spend more time playing video games; sales and consumption of video games skyrocketed, breaking previous records worldwide. Existing theoretical perspectives suggest one possible reason for this popularity: video games, including single-player video games, may help people feel socially connected. For example, according to the bi-dimensional rejection taxonomy, solo gameplay is a disengaged prosocial response, an attempt to replenish belonging in a hands-off, indirect manner. Also, according to the social surrogacy hypothesis, solo gameplay can provide social surrogates, symbolic bonds that can replenish belonging. Players can form parasocial relationships (one-way psychological bonds) with a non-player character in the game; players can also immerse themselves in the social worlds and feel like a member of a collective presented in the video game. Although existing theories and qualitative evidence suggest that solo gameplay can benefit belonging, quantitative evidence is lacking to support this prediction. In this dissertation, I examined if solo gameplay could replenish belonging after social rejection. In Study 1, I validated the Heart Manikin—a single-item measure of state belonging, which I used in the subsequent studies. In Study 2, rejected participants recalled their time playing a video game with vs. without social surrogates. In Study 3, rejected participants played a custom video game that manipulates parasocial relationships and social worlds. Across studies, I found that rejected participants reported similar levels of belonging after being exposed to social surrogates in video games. The results move forward the discourse on the bi-dimensional rejection taxonomy, the social surrogacy hypothesis, and the video games literature."
acknowledgements: ""
site: bookdown::bookdown_site
# documentclass for the UD thesis style ------
documentclass: udthesis
# documentclass: book
output:
  bookdown::gitbook:
    lib_dir: "book_assets"
    config:
      edit:
        link: https://github.com/nsunami/dissertation/edit/master/%s
        text: "Edit"
      sharing:
        github: yes
        facebook: no 
  bookdown::pdf_book:
    template: "latex/default.latex"
    keep_tex: yes
    latex_engine: xelatex
    includes:
      in_header: "latex/preamble.tex"
      before_body: "latex/approval-page.tex"
    pandoc_args: [--top-level-division=chapter]
    toc: no
    toc_appendix: yes
  # bookdown::word_document2:
  #   toc: no
  #   toc_appendix: yes
bibliography: [references.bib, packages.bib]
csl: "apa.csl"
link-citations: true
github-repo: "nsunami/dissertation"
delete_merged_file: false
always_allow_html: true
---

```{r bidr-setup, message=FALSE, warning=FALSE, include=FALSE}
# Chunk Options
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
# Load rmarkdown package to get `metadata`
library(rmarkdown)
```

```{r, echo=FALSE}
library(tidyverse)
library(metathis)
meta() %>%
  meta_description(
    "Nami Sunami's Doctoral Dissertation on Video Games and Belonging "
  ) %>% 
  meta_name("github-repo" = "nsunami/dissertation") %>% 
  meta_viewport() %>% 
  meta_social(
    title = "Playing Alone, Feeling Connected: Do Single-Player Video Games with Social Surrogates Replenish Belonging After Social Rejection?",
    url = "https://nsunami.github.io/dissertation/",
    image = "https://raw.githubusercontent.com/nsunami/dissertation/2f48c254e6c6ebe7410fde51f0dcaf28e9c4779c/img/og.png",
    image_alt = "The title image of the dissertation",
    og_type = "book",
    og_author = "Naoyuki Sunami",
    twitter_card_type = "summary",
    twitter_creator = "@n_sunami"
  )

```



# Overview

People have a fundamental need to belong---to be accepted, loved, and
cared for [@baumeisterNeedBelongDesire1995; @maslow1943]. Being forced to stay at home
during the COVID-19 pandemic, many people experienced threats to
belonging: an experience of feeling rejected, excluded, and unloved. At
the same time, more and more people bought and played video games.
Worldwide spending and Google search interests on video games hit an
all-time high for March, April, and May in 2020, coinciding with the
stay-at-home orders in the US [@beresford2020; @shanley2020;
@superdatastaff2020]. Media reports have suggested that people play
video games to cope with social isolation during the COVID-19 crisis
[@baraniuk2020; @gregory2020; @langille2020; @lazarus2020]. Existing
research supports that playing video games with others online (e.g., in
a multiplayer mode) can increase belonging [@kowert2015; @vella2015].
However, people can also play alone in a single-player mode (solo play),
and whether solo plays can increase belonging remains unknown.
Theoretically, solo plays can help people feel socially connected
through social surrogates: parasocial relationships with non-player
characters and social worlds where players can immerse themselves and
feel like a member of a collective in the game. This raises an empirical
question: Can a player replenish their belonging even when they play
alone themselves? I designed my dissertation to answer this question.

I structure my dissertation as follows. In Chapter 2, I present my
published work on the bi-dimensional rejection taxonomy [@sunamiBIDimensionalRejectionTaxonomy2020]
to highlight the need for more evidence on the disengaged-prosocial
responses: indirect, and hands-off attempts that increase belonging. In
Chapter 3, I suggest that playing a video game in a single-player mode
is an unexamined disengaged-prosocial response to social rejection. I
draw from the social surrogacy hypothesis [@gabrielSocialSurrogatesRejection2017] and the video
games literature to suggest that solo plays can fulfill belonging. In
Chapter 4 (Study 1), I first validated the Heart Self-Assessment Manikin
(Heart Manikin), a single-item pictorial measure of belonging that I
used as a key outcome for Studies 2 and 3. In Chapter 4 (Study 2), I
examined whether recalling a video game with vs. without social
surrogates, would increase belonging following social rejection. In
Chapter 5 (Study 3), I let participants play a custom-made,
single-player role-playing game to examine whether parasocial
relationships or social worlds replenish belonging after social
rejection. In Chapter 6, I discuss the findings of my dissertation and
future avenues for research.
